Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
Update paper.qmd

>>>>

```
The results of the US elections in large part hinge on the direction of the swing states. A swing state is a state that holds a significant number of electoral votes and could reasonable be won by either Trump or Harris. [FIG] shows the probability that both candidates have of winning each of the 7 swing states.

```{r plot-probabilities, echo=FALSE, fig.width=8, fig.height=6}
# Reshape the data for plotting
swing_long <- swing_probs %>%
  pivot_longer(cols = c("Trump", "Harris"), names_to = "Candidate", values_to = "Probability")

custom_colors <- c("Trump" = "#DD1717", "Harris" = "#0F4392")

# Create the bar plot
ggplot(swing_long, aes(x = state, y = Probability, fill = Candidate)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = custom_colors) +
  labs(
    title = "Probability of Winning Swing States",
    x = "State",
    y = "Probability (%)",
    fill = "Candidate"
  ) +
  theme_minimal() +
  theme(
    text = element_text(size = 12),
    plot.title = element_text(hjust = 0.5)
  )
